Noisy Work: A Review of The Uncertainty Visualisation Literature

### 2024-03-17 paper.qmd
small edit

### Contextual Information
Some uncertainty work, specifically uncertainty visualisation, focus on the context surrounding the uncertainty, such as the spatial or temporal nature of the estimate. While other discussions of uncertainty may consider this distinction more relevant to their work, here we will consider this contextual information. Contextual information is important for interpretation and understanding of graphics, but it does not in of itself generate uncertainty. Its relevance to the field of "uncertainty visualisation" is through the percieved lack of available channels. For example, a choropleth map has already used colour to represent an estimate, and the concept of space to provide contextual information, there is little remaining room tany spatial

>>>>

### Contextual Information
One of the key components of uncertainty and inference is the noise and signal dichotomy. We can only identify which pieces of information contain signal in relation to a signal of interest, the uncertainty around that signal (or noise) is not a

Some uncertainty work, specifically uncertainty visualisation, focus on the context surrounding the uncertainty, such as the spatial or temporal nature of the estimate. While other discussions of uncertainty may consider this distinction more relevant to their work, here we will consider this contextual information. Contextual information is important for interpretation and understanding of graphics, but it does not in of itself generate uncertainty. Its relevance to the field of "uncertainty visualisation" is through the percieved lack of available channels. For example, a choropleth map has already used colour to represent an estimate, and the concept of space to provide contextual information, there is little remaining room tany spatial
